\chapter{Literature Review}\label{ch:citations}

This chapter should be linked to PO(b), Identify, formulate, research literature, interpret data, and analyze complex electrical and electronic engineering problems using principles of mathematical, natural and engineering sciences.

In this chapter we show how we can cite the references.


\section{See the Citations}
\label{sec:cite}

According to \cite{karim2023reconfigurable}, a reconfigurable broadband metasurface was developed with switchable functionalities in the visible range. In a comprehensive review by \cite{himel2023biomimicry}, the authors discussed the concept of biomimicry in nanotechnology. The work of \cite{bhuiyan2022tin} presented an all-optical reflection modulator reaching 85\% efficiency for the 2$\mu$m waveband. Roy et al. \cite{roy2022custom} developed a custom gold-patterned rewritable optical disc-based plasmonic sensor for blood hemoglobin detection. The refractive index sensor based on a T grating on a nano-cavity array was presented by \cite{abed2021t}. In the field of virus detection, \cite{hassan2021review} provided a review on plasmonic nano-biosensors with a focus on coronavirus. The work of \cite{sarker2020structurally} introduced a structurally tunable gear-shaped plasmonic sensor. A comprehensive review on colors with plasmonic nanostructures was presented by \cite{song2019colors}. The roadmap on metasurfaces was outlined by \cite{quevedo2019roadmap}. The sensitivity to ambient refractive index was enhanced using tunable few-layer graphene/hBN nanoribbons \cite{jiang2019enhancing}. Jiang et al. \cite{jiang2019modulating} demonstrated phase modulation with metasurfaces using gated ultra-thin TiN films. The material platforms for optical metasurfaces were discussed in \cite{choudhury2018material}. Hybrid plasmonic waveguides formed by metal coating of dielectric ridges were investigated by \cite{zenin2017hybrid}. A Pancharatnam-Berry phase manipulating metasurface for visible color hologram based on low-loss silver thin film was presented by \cite{choudhury2017pancharatnam}. Kim et al. \cite{kim2016controlling} controlled the polarization state of light with plasmonic metal oxide metasurfaces.


\endinput



