\chapter{Evaluation}\label{safeklabelingpetersen}

\section{Assessment of Issues}
In this section, Apply reasoning to assess societal, health, safety, legal and cultural issues and the consequent responsibilities relevant to professional engineering practice and solutions particular to your thesis.

Should be linked to PO(f) The Engineer and Society: Apply reasoning to assess societal, health, safety, legal and cultural issues and the consequent responsibilities relevant to professional engineering practice and solutions to complex engineering problems. (K7).
\subsection{Societal Issues}

\subsection{Health and Safety Issues}

\subsection{Legal and Cultural Issues}

\section{Evaluation of Environment and Sustainability}

In this section, evaluate the sustainability and impact of your thesis work in societal and environmental contexts. 

Should be linked to PO(g) Environment and sustainability: Understand and evaluate the sustainability and impact of professional engineering work in the solution of complex engineering problems in societal and environmental contexts. (K7).

\section{Ethical Issues}

In this section, clearly mention how ethical principles and commitment to professional ethics and responsibilities was upheld during your thesis work. Mention responsible conduct of research, plagirism etc.

Should be linked to PO(h) Ethics: Apply ethical principles and commit to professional ethics and responsibilities and norms of engineering practice. (K7).

\section{Future Works}

In this section, discuss possible future works for your particular thesis work. 

Should be linked PO(l) Life-long Learning: Recognize the need for, and ability to engage in life-long learning and know contemporary aspects related to the field of electrical and electronic engineering.
\endinput

